Sparse Function-space Representation \\ of Neural Networks

### 2023-05-17 paper/main.tex
small thing

%% Comments on the results:
From \cref{tbl:cl_table_1}, it is clear that the weight-space regularization methods fail entirely compared to the function-space methods on S-MNIST and S-FMNIST but are still able to achieve reasonable results on P-MNIST. %, commonly referred to as Domain Incremental Learning. (opposed to the Class-Incremental Learning for S-MNIST and S-FMNIST)
Considering only function-space methods, we can see that \our achieves the best results on most data sets and is particularly effective when using fewer points per task.
On S-FMNIST, our method obtains close results to DER, which regularizes the model by taking the mean squared error between current and old function outputs without accounting for the covariance structure of the loss similar to our L2 ablation. However, DER differs from our ablation since it resorts to a reservoir sampling \citep{vitter1985random} to continuously update the set of points instead of picking them at the task boundary.
Finally, \our-based regularizer obtains comparable results to the best-performing method on P-MNIST, S-FSVI, which has the downside of requiring computational intensive based on performing variational inference, compared to \our. \todo{on PMNIST our method is not really super-fast, so that could be not the best thing to say here} % we could also say that P-MNIST is known to be a bad/ill-posed data set for CL 
Finally, it is worth noticing as our ablation already provides a very solid baseline consistently over all data sets.

>>>>

%% Comments on the results:
From \cref{tbl:cl_table_1}, it is clear that the weight-space regularization methods fail entirely compared to the function-space methods on S-MNIST and S-FMNIST but are still able to achieve reasonable results on P-MNIST. %, commonly referred to as Domain Incremental Learning. (opposed to the Class-Incremental Learning for S-MNIST and S-FMNIST)
Considering only function-space methods, we can see that \our achieves the best results on most data sets and is particularly effective when using fewer points per task.
On S-FMNIST, our method obtains close results to DER, which regularizes the model by taking the mean squared error between current and old function outputs without accounting for the covariance structure of the loss similar to our L2 ablation. However, DER differs from our ablation since it resorts to a reservoir sampling \citep{vitter1985random} to continuously update the set of points instead of picking them at the task boundary.
Finally, \our-based regularizer obtains comparable results to the best-performing method on P-MNIST, S-FSVI, which has the downside of requiring computational intensive based on performing variational inference, compared to \our. \todo{on PMNIST our method is not really super-fast, so that could be not the best thing to say here} % we could also say that P-MNIST is known to be a bad/ill-posed data set for CL 
Finally, it is worth noticing our ablation already provides a very solid baseline consistently over all data sets.
